Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2014-01-08 paper/main.tex
structure paragraph, methods description, new references

\title[Vweb \& Tweb]{Cosmic web correlations with the shape, spin and
  peculiar velocties of dark matter halos}  
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Sergio Contreras$^{1}$ 
  Jaime E. Forero-Romero$^{1}$ 
  Nelson Padilla$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

The structure of this \documentname is the following.

@@

... There is abundant literature on the issue of shape and angular momentum
aligmnent of dark matter haloe with respect to the cosmic we.

@@

... Table 1 and Table 2 summarizes recent results found in the literature for
shape and angular momentum alignment.

@@

\section{N-body simulation and halo finding}

@@

\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
  r_{\alpha}\partial r_{\beta}}, 
\end{equation}
where $\phi$ is the gravitational potential rescaled by a factor $4\pi
G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
equation can be written as:

\begin{equation}
\nabla^{2}\phi  = \delta, 
\end{equation}

where $\delta$ is the matter overdensity, $\bar{\rho}$ is the average
matter density, $H_{0}$ is the Hubble constant at present time and
$\Omega_m$ is the matter density parameter.

@@

\begin{equation}
\Sigma_{\alpha\beta} = -\frac{1}{2H_{0}}\left(\frac{\partial
  v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
  r_{\alpha}}\right) 
\end{equation}

@@

In this paper we compute the cosmic web on grids of two different
resolutions $256^3$ and $512^3$. In the case for the Tweb we interpolate

\section{Results}

>>>>

\title[Vweb \& Tweb]{Cosmic web correlations with the shape, spin and
  peculiar velocties of dark matter halos}  
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Jaime E. Forero-Romero$^{1}$,
  Sergio Contreras$^{2}$,
  Nelson Padilla$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

The structure of this \documentname is the following. In \S
\ref{sec:theory} we present the theoretical antecedendts for the
alignment studies we present in this paper. In \S
\ref{sec:nbody} we present the N-body
cosmological simulation and halo catalogs next to describe in
\S\ref{sec:algorithms} the two web-finding algorithms we use. In
\S\ref{sec:results} we present our main results about the alignment
of shape, spin and peculiar velocities with respect to the cosmic
web. We continue with a discussion of these results in
\S\ref{sec:discussion} paying special attention to resolution effects
and the conditions that might drive the strong alignment signals
observed in the precedent section. In \S\ref{sec:conclusions} we
present our conclusions.

@@

... There is abundant literature on the issue of shape and angular momentum
aligmnent of dark matter haloe with respect to the cosmic web.

@@

... Table 1 and Table 2 summarizes recent results found in the literature for
shape and angular momentum alignment. The Appendix includes a detailed
description of each one the algorithms.

The main summary from these results can be done in three points. (i)
The halo mass of $1-5\times 10^{12}$\hMsun is a threshold mass between
different behaviours.  (ii) Halo shape is strongly aligned along
filaments, more so for massive haloes and (iii) Halo spin tends to be
perpendicular with respect to filaments, but it is a weak.

@@

\section{N-body simulation and halo finding}
\label{sec:nbody}

@@

\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
  r_{\alpha}\partial r_{\beta}}, 
\end{equation}
%
where $\phi$ is the gravitational potential rescaled by a factor $4\pi
G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
equation can be written as $\nabla^{2}\phi  = \delta$, where $\delta$
is the matter overdensity, $\bar{\rho}$ is the averagematter density,
$H_{0}$ is the Hubble constant at present time and $\Omega_m$ is the
matter density parameter. A detailed presentation of this algorithm
can be found in \citep{Tweb}.

@@

\begin{equation}
\Sigma_{\alpha\beta} = -\frac{1}{2H_{0}}\left(\frac{\partial
  v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
  r_{\alpha}}\right), 
\end{equation}
%
where $v_{\alpha}$ correspond to the components of the peculiar
comoving velocities. With this definition the trace of the shear
tensor is minus the divergence of the velocity field normalized by the
Hubble constant $-\nabla\cdot {\bf}v /H_{0}$. A detailed description
of this algorithm can be found in \citep{Vweb}.

@@

In this paper we compute the cosmic web on grids of two different
resolutions $256^3$ and $512^3$. In the V-Web computations we compute
the velocity field as follows. First we compute the momentum density field
over a grid and the normalize it by the matter density field. We follow the
same procedure for the gaussian smoothed fields. It means that a
smoothed velocity fields is the ratio of the smoothed momentum density
and matter density fields.

\section{Results}
\label{sec:results}
